Spfy: an integrated graph-based sequence database for real-time prediction of Escherichia coli phenotypes

### 2018-01-30 paper-webserver.tex
EDIT: merged 2 functionality paragraphs

By supporting multiple \textit{in-silico} subtyping options, the platform functions similar to a reference laboratory, while adding support for population analyses. Subtyping options for E.coli are O-antigen, H-antigen, Shiga-toxin 1 (Stx1), Shiga-toxin 2 (Stx2), and Intimin typing, VF and AMR annotation, pan-genome generation, group comparisons via Fisher's, and machine-learning (ML) based predictions for OmniLog AMR assays. These tasks are divided into subtasks, and distributed across a built-in task queue. Results are also decomposed into graph structures and stored within a larger graph database. By integrating task distribution with graph storage, Spfy enables large-scale analyses, such as epidemiological associations between specific genotypes, biomarkers, host, source, and other metadata, and statistical significance testing of genome markers for user-defined groups, in real-time. Currently, the platform has been tested with XXX genome files and result storage for XX analyses modules.

% Need a sentance introducing the tools otherwise this sounds just like the intro section
Prebuilt tools are available for a variety of reference laboratory tasks.
Spfy performs: O-antigen typing, H-antigen typing, and VF gene determination using ECtyper \url{https://github.com/phac-nml/ecoli\_serotyping}, STX typing using Phylotyper \cite{whiteside2017phylotyper}, and AMR gene determination using the RGI program \cite{mcarthur2013comprehensive}. Spfy also performs bioinformatics analyses: pangenome generation using Panseq \cite{laing2010pan}, statistical significance testing using SciPy \cite{jones2014scipy}, and support vector machine (SVM)-backed AMR predictions using Scikit-learn \cite{pedregosa2011scikit}.
For the larger population comparisons, we store and aggregate the results from individual genome analyses.

>>>>

By supporting multiple \textit{in-silico} subtyping options, the platform functions similar to a reference laboratory, while adding support for population analyses. Subtyping options for E.coli are O-antigen, H-antigen, and VF gene determination using ECtyper \url{https://github.com/phac-nml/ecoli\_serotyping}, Shiga-toxin 1 (Stx1), Shiga-toxin 2 (Stx2), and Intimin typing using Phylotyper \cite{whiteside2017phylotyper}, and AMR annotation using the RGI program \cite{mcarthur2013comprehensive}.
Spfy also performs bioinformatics analyses: pangenome generation using Panseq \cite{laing2010pan}, statistical significance testing using SciPy \cite{jones2014scipy}, and support vector machine (SVM)-backed AMR predictions for OmniLog AMR assays using Scikit-learn \cite{pedregosa2011scikit}.

These tasks are divided into subtasks, and distributed across a built-in task queue. Results are converted to individual graphs and stored within a larger graph database. By integrating task distribution with graph storage, Spfy enables large-scale analyses, such as epidemiological associations between specific genotypes, biomarkers, host, source, and other metadata, and statistical significance testing of genome markers for user-defined groups, in real-time. Currently, the platform has been tested with XXX genome files and result storage for XX analyses modules.
